---
title: "histAlp"
author: "Michael Kahle"
date: "31 1 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

http://www.zamg.ac.at/histalp/dataset/station/csv.php


Auer I, Böhm R, Jurkovic A, Lipa W, Orlik A, Potzmann R, Schöner W, Ungersböck M, Matulla C, Briffa K, Jones PD, Efthymiadis D, Brunetti M, Nanni T, Maugeri M, Mercalli L, Mestre O, Moisselin J-M, Begert M, Müller-Westermeier G, Kveton V, Bochnicek O, Stastny P, Lapin M, Szalai S, Szentimrey T, Cegnar T, Dolinar M, Gajic-Capka M, Zaninovic K, Majstorovic Z, Nieplova E, 2007. HISTALP – Historical instrumental climatological surface time series of the greater Alpine region 1760-2003. International Journal of Climatology 27: 17-46 


```{sh downloads}

for station in "GRA" "INN" "WRN"
do
  for parameter in "T01" "R01"
  do
     file="histalp_${station}_${parameter}.csv"
     data="station=_1&statabbr=${station}&parameter=${parameter}&exportCSV=export+Data+as+CSV&season=year"
     echo "Download file: $file"
     echo $mkmkmk
     [ -f ./download/$file ] && mv -f ./download/$file ./download/$file.bck
     curl "http://www.zamg.ac.at/histalp/dataset/station/csv.php"  --data "$data" > ./download/$file
     ## Remove first 4 lines !!
     tail -n +5 ./download/$file > ./download/$file.tmp && mv ./download/$file.tmp   ./download/$file
     ## Remove complete empty lines
     grep -v "999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999;999999" ./download/$file > ./download/$file.tmp && mv ./download/$file.tmp   ./download/$file
  done
done
```


```{r read}

for (station in c("GRA","INN","WRN")){
  print(paste("Reading station:", station))
  fileT <- paste("./download/histalp_", station, "_T01.csv", sep="")
  temp <- read.csv(fileT, sep=";", na = "999999", comment.char="#")
  fileP <- paste("./download/histalp_", station, "_R01.csv", sep="")
  prec <- read.csv(fileP, sep=";", na = "999999", comment.char="#")
}

# T in 0.1 degree, convert to monthly series...

```

